---
title: "Country Summary: Togo"
header-includes:
  - \usepackage{pdfpages}
output: 
  pdf_document:
    toc: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(root.dir = "/Users/j_godwin/Dropbox/AfricaAdmin2Estimates/Data/countryDataFolders")

dir.path <- "/Users/j_godwin/Dropbox/AfricaAdmin2Estimates/Data/countryDataFolders"

logit <- function(x){
  log(x/(1-x))
}
expit <- function(x){
  exp(x)/(1 + exp(x))
}

```

```{r params, echo = F}
country <- "Togo"
CountryList <- read.csv(paste0(dir.path,
                               '/CountryList.csv'), header = T)
folder.name <- CountryList$folderName[CountryList$Country == country]

gadm.abbrev <- CountryList$gadmCode[CountryList$Country == country]
n.survey <- CountryList$nSurvey[CountryList$Country == country]
HIV.sheet <- read.csv(paste0(dir.path ,
                             "/HIV.csv"), header = T)
HIV.country <- as.data.frame(HIV.sheet[HIV.sheet$Country == country,])

useHIVAdj <- (unique(HIV.country$MM.Adj.by.IGME) == "Y" &
                unique(HIV.country$UNAIDS.data.) == "Y")
SurveyInfo <- read.csv(paste0(dir.path,
                              "/SurveyInfo.csv"), header = T)
surveys <- SurveyInfo$Survey.Year[SurveyInfo$Country == country &
                                    SurveyInfo$`GPS.` == "Y"]
survey.legends <- SurveyInfo$`OfficialSurveyName`[SurveyInfo$Country == country &
                                                    SurveyInfo$`GPS.` == "Y"]

load(paste0(dir.path,'/',
            folder.name,
            '/shapeFiles_gadm/',
            country,
            '_Amat.rda'))
load(paste0(dir.path,'/',
            folder.name,
            '/shapeFiles_gadm/',
            country,
            '_Amat_Names.rda'))

```
# Intro

These estimates are created using the BB8 model with Admin 2 estimates using a RW1xICAR interaction model with area-specific random slopes. \par


`r country` has `r nrow(admin1.names)` Admin 1 areas and `r nrow(admin2.names)` Admin 2 areas.\par


All uncertainty intervals displayed in subsequent figures are 95\% intervals.

\begin{figure}
\centering
\includegraphics[width=3.5in]{/Users/j_godwin/Dropbox/AfricaAdmin2Estimates/Data/countryDataFolders/Togo/Plots/ShapeCheck/Togo_adm2_neighb.pdf}
\includegraphics[width=3.5in]{/Users/j_godwin/Dropbox/AfricaAdmin2Estimates/Data/countryDataFolders/Togo/Plots/ShapeCheck/Togo_Admin2Names.pdf}
\caption{Top: The neighborhood structure of Admin 2 areas. Bottom: The names of Admin 2 areas.}
\end{figure}
\clearpage

\begin{figure}
\centering
\includegraphics[width=5in]{/Users/j_godwin/Dropbox/AfricaAdmin2Estimates/Data/countryDataFolders/Togo/Plots/Betabinomial/map/Togo_rw2main_randomSlopes_rw1xICAR_admin2_NotStrat_2019_median.pdf}
\caption{Median estimates of U5MR (deaths per 1000 children) in 2019.}
\end{figure}
\begin{figure}
\centering
\includegraphics[width=3.5in]{/Users/j_godwin/Dropbox/AfricaAdmin2Estimates/Data/countryDataFolders/Togo/Plots/Betabinomial/measure/Togo_rw2main_randomSlopes_rw1xICAR_admin2_NotStrat_Y2019_K2_measuremap.pdf}
\includegraphics[width=3.5in]{/Users/j_godwin/Dropbox/AfricaAdmin2Estimates/Data/countryDataFolders/Togo/Plots/Betabinomial/measure/Togo_rw2main_randomSlopes_rw1xICAR_admin2_NotStrat_Y2019_K3_measuremap.pdf}
\caption{Expression of uncertainty of U5MR (deaths per 1000 children) based on the average true classification probability (ATCP) in 2019.}
\end{figure}
\clearpage

\begin{figure}
\centering
\includegraphics{/Users/j_godwin/Dropbox/AfricaAdmin2Estimates/Data/countryDataFolders/Togo/Plots/Betabinomial/map/Togo_rw2main_randomSlopes_rw1xICAR_admin2_NotStrat_19902019_median.pdf}
\caption{Median estimates for selected years.}
\end{figure}
\clearpage

\clearpage

\includepdf[pages={-}]{/Users/j_godwin/Dropbox/AfricaAdmin2Estimates/Data/countryDataFolders/Togo/Plots/Betabinomial/Admin2/Togo_rw2main_randomSlopes_rw1xICAR_admin2Bench_spaghetti_allByMedian.pdf}

\begin{figure}
\centering
\includegraphics{/Users/j_godwin/Dropbox/AfricaAdmin2Estimates/Data/countryDataFolders/Togo/Plots/Betabinomial/ridge/Togo_rw2main_randomSlopes_rw1xICAR_admin2_NotStrat_2019_ridgeplot.pdf}
\caption{Posterior distributions of U5MR (deaths per 1000 children) in 2019. Areas are ordered by median estimated U5MR in 2019.}
\end{figure}
\clearpage
\begin{figure}
\centering
\includegraphics[height=10in]{/Users/j_godwin/Dropbox/AfricaAdmin2Estimates/Data/countryDataFolders/Togo/Plots/Betabinomial/map/Togo_rw2main_randomSlopes_rw1xICAR_admin2_NotStrat_median.pdf}
\caption{Posterior medians of U5MR (deaths per 1000 births) by Admin 2 area and year.}
\end{figure}
\clearpage



# National Survey Data
```{r sumstat, echo = F,results='asis', warning=FALSE}
library(xtable)
load(paste0(dir.path, '/',
            folder.name, '/',
            country,
            '_cluster_dat.rda'))
levels(mod.dat$urban) <- tolower(levels(mod.dat$urban))
clus.table <- aggregate(cluster ~ survey + urban,
                        data = mod.dat,
                        FUN = function(x){length(unique(x))})
clus.xtable <- reshape(clus.table,
                       v.names = "cluster",
                       idvar = "survey",
                       timevar = "urban",
                       direction = "wide")
clus.xtable$Total <- clus.xtable$cluster.urban + 
  clus.xtable$cluster.rural
row.names(clus.xtable) <- clus.xtable[,'survey']
survey_names <- as.character(rev(survey.legends))
survey_names <- sapply(survey_names, 
                       function(x){substr(x, start=5, stop=nchar(x))})
clus.xtable$survey <- survey_names
colnames(clus.xtable) <- c("Survey", "Urban",
                           "Rural", "Total")
clus.printxtable <- xtable(clus.xtable, 
                           digits = c(0,0,0,0,0),
                           align = "ccccc",
                           caption = paste0("Number of clusters by urban/rural designation by survey for ",
                                            country, "."))
print.xtable(clus.printxtable, 
             comment = F, 
             include.rownames = F)

sum.table <- aggregate(cbind(Y, total) ~ survey + age,
                       data = mod.dat,
                       FUN = sum)
sum.tableList <- list()
idx <- 0
for(i in 1:length(surveys)){
  idx <- idx + 1
  survey <- surveys[i]
  sum.tableList[[idx]] <- sum.table[sum.table$survey == survey,-1]
  names(sum.tableList[[idx]]) <- c("Age", 
                                   "No. Deaths",
                                   "No. Agemonths")
  
  sum.print <- xtable(sum.tableList[[idx]],
                      digits = c(0,0,0,0),
                      align = "cccc", 
                      caption = paste0("Numbers of agemonths and deaths by age for ",
                                       survey.legends[i], "."))
  print.xtable(sum.print,
               comment = F,
               include.rownames = F,
               table.placement = "!ht")
}
```

\clearpage

# Admin 2 Figures

The following few pages have estimates by area across time with underlying data included. There are six admin areas per page.
<!-- ,they are ordered by increasing median U5MR in the year 2019.  -->
Colored lines with circular points and light grey uncertainty bands are 5-year survey-weighted estimates of U5MR for years 1990--1994 up to 2015--2019 depending on survey timing. For a survey that ends in the middle of a 5-year period, we plot the estimates at the mid-point of the years in that interval for which the survey provides data. Black lines and corresponding intervals represent posterior medians and 95\% uncertainty intervals respectively for the betabinomial model.
<!-- IHME's estimates and corresponding intervals, where we can compare, are in aquamarine. -->

\includepdf[pages=-]{/Users/j_godwin/Dropbox/AfricaAdmin2Estimates/Data/countryDataFolders/Togo/Plots/Betabinomial/Admin2/Togo_rw2main_randomSlopes_rw1xICAR_admin2Bench_noStrata_spaghetti_6per.pdf}





# National Figures and Results
```{r, results ='asis', echo = FALSE}
load(paste0(dir.path, '/',
            folder.name, '/',
            country,
            '_rw2_natl_noStrata_fixed.rda'))
coefs <- fixed.eff

load(paste0(dir.path, '/',
            folder.name, '/',
            country,
            '_rw2_natlBench_noStrata_fixed.rda'))
coefs.bench <- fixed.eff

coefs$tab <- paste0("(",
                    round(expit(coefs$`0.025quant`)*1000,1),
                    ",",
                    round(expit(coefs$`0.975quant`)*1000,1),
                    ")")
coefs <- coefs[,c("0.5quant", "tab")]
coefs$`0.5quant` <- round(expit(coefs$`0.5quant`)*1000,1)

coefs.bench$tab <- paste0("(",
                          round(expit(coefs.bench$`0.025quant`)*1000,1),
                          ",",
                          round(expit(coefs.bench$`0.975quant`)*1000,1),
                          ")")
coefs.bench <- coefs.bench[,c("0.5quant", "tab")]
coefs.bench$`0.5quant` <- round(expit(coefs.bench$`0.5quant`)*1000,1)

names(coefs) <- c("Median", "Interval")
names(coefs.bench) <- c("Median- Bench", "Interval")

row.names(coefs) <- row.names(coefs.bench) <- c("0", "1-11", "12-23",
                                                "24-35", "36-47", "48-59")

coefs.xtable <- xtable(cbind.data.frame(coefs, coefs.bench),
                       align = c("l|cc|cc"),
                       digits = c(0,2,0,2,0),
                       caption = paste0("Monthly hazards in terms of 1000 children by age band for national, unstratified model for ", country, "."))
print.xtable(coefs.xtable,
             comment = F)
```


\begin{figure}
\centering
\includegraphics{/Users/j_godwin/Dropbox/AfricaAdmin2Estimates/Data/countryDataFolders/Togo/Plots/Betabinomial/National/Togo_rw2_natlBenchmarks.pdf}
\caption{Benchmark offsets: $
\mbox{BENCH}(t) = \mbox{U5MR}^\star(t)/\mbox{U5MR}(t)$
where $\mbox{U5MR}^\star(t)$ is modeled estimate and  $\mbox{U5MR}(t)
$ is UN-IGME estimate.}
\end{figure}


\begin{figure}
\centering
\includegraphics{/Users/j_godwin/Dropbox/AfricaAdmin2Estimates/Data/countryDataFolders/Togo/Plots/Betabinomial/National/Togo_rw2_natlBench_temporal.pdf}
\caption{Monthly hazards of death in terms of U5MR (number deaths per 1000 children) by agebands.}
\end{figure}
\clearpage

\begin{figure}
\centering
\includegraphics{/Users/j_godwin/Dropbox/AfricaAdmin2Estimates/Data/countryDataFolders/Togo/Plots/Betabinomial/National/Togo_rw2_natlBench_noStrata_spaghetti.pdf}
\caption{Benchmarked U5MR rates per 1000 live births. Top: DHS direct estimates with national trends from IHME GBD, UN-IGME, Smoothed Direct and Betabinomial estimates. Middle: 95\% uncertainty intervals for DHS data. Bottom: IHME GBD, UN-IGME, Smoothed Direct and Betabinomial estimates with for the unstratified model. 95\% uncertainty intervals}
\end{figure}
\clearpage



# Admin 1 Figures

\includepdf[pages=-]{/Users/j_godwin/Dropbox/AfricaAdmin2Estimates/Data/countryDataFolders/Togo/Plots/Betabinomial/Admin1/Togo_rw2main_randomSlopes_rw1xICAR_admin1Bench_noStrata_spaghetti_6per.pdf}

