---
title: "Country Summary: Senegal"
output: 
  pdf_document:
    toc: true
    number_sections: true
---


<!-- Setup -->

<!-- Libraries -->

```{r libs, echo = FALSE, message=FALSE, warning=FALSE}
rm(list = ls())

options(gsubfn.engine = "R")
library(rgdal)
library(Rfast)
library(dplyr)
library(tidyr)
library(ggplot2)
library(tidyverse)
library(RColorBrewer)
library(xtable)

## knitr options
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
```

<!-- User-defined Arguments -->
```{r params}
country <- "Senegal"
debugging <- FALSE

## MIGHT NEED TO BE CHANGED depending on what you fit
time.model <- c('rw2','ar1')[2]
strata.model <- c("strat", "unstrat")[1]
bench.model <- c("", "bench")[1]


## Timing of projection

end.proj.year <- 2021
plot.years <- 2000:end.proj.year
n_years <- length(plot.years)
```


<!-- Working Directory -->

```{r setwd}

# set the working directory (location of this file in /Rcode)

# extract file location of this script
code.path <- rstudioapi::getActiveDocumentContext()$path
code.path.splitted <- strsplit(code.path, "/")[[1]]

home.dir <- paste(code.path.splitted[1: (length(code.path.splitted)-3)],
                  collapse = "/")


knitr::opts_chunk$set(root.dir = home.dir)

if(debugging == TRUE){
  setwd(home.dir)
}

# set the directory that stores the data

# data.dir <- paste0(home.dir,'/Data/', country) 
data.dir <- paste0("R://Project/STAB/", country)

# set the directory to store the results (e.g. fitted R objects, figures, tables in .csv etc.)

res.dir <- paste0(home.dir,'/Results/', country)
```


<!-- ## Functions -->
```{r fns}
logit <- function(x){
  log(x/(1-x))
}
expit <- function(x){
  exp(x)/(1 + exp(x))
}

##### function to organize posterior draws from BB8 ####

draw_1y_adm<-function(admin_draws, year_num,admin_vec, nsim=1000){
  
  # year_num: year of comparison
  # nsim: number of posterior draws
  # admin_vec: vector of admin index
  # admin_draws: posterior draws (as a list from SUMMER output)
  
  # prepare reference frame for draws 
  # ID corresponds to specific year, region
  draw_ID<-c(1:length(admin_draws))
  draw_year<-vector()
  draw_region<-vector()
  
  for( i in draw_ID){
    tmp_d<-admin_draws[[i]]
    draw_year[i]<-tmp_d$years
    draw_region[i]<-tmp_d$region
  }
  
  draw_ref<-data.frame(id=draw_ID,year=draw_year,
                       region=draw_region)
  
  draw_frame<-matrix( nrow = nsim, ncol = length(admin_vec))
  
  for(i in 1:length(admin_vec)){
    admin_i<-admin_vec[i]
    id_draw_set<-draw_ref[draw_ref$year==year_num&
                            draw_ref$region==admin_i,]$id 
    
    draw_set<-admin_draws[[id_draw_set]]$draws
    
    draw_frame[,i]<-draw_set
    #print(mean(r_frame[,c(admin_i)]))
  }
  
  colnames(draw_frame)<-admin_vec
  
  return(draw_frame)
}

```

<!-- # Load Data: Country Info -->


```{r load_countryinfo, echo = FALSE}
info.name <- paste0(country, "_general_info.Rdata")

# load the country info

info.name <- paste0(country, "_general_info.Rdata")
load(file = paste0(home.dir, '/Info/', info.name, sep=''))
```

<!-- #### Load admin names  ------------------------------------------------------ -->

```{r load_adminnames}
load(paste0(data.dir, '/',poly.path,'/', country, '_Amat.rda'))
load(paste0(data.dir, '/', poly.path,'/', country, '_Amat_Names.rda'))
```



<!-- #### load admin1 and admin2 weights #### -->
```{r load_adminwts}
load(paste0(data.dir,'/worldpop/adm1_weights_u1.rda'))
load(paste0(data.dir,'/worldpop/adm1_weights_u5.rda'))
if(exists('poly.layer.adm2')){
  load(paste0(data.dir,'/worldpop/adm2_weights_u1.rda'))
  load(paste0(data.dir,'/worldpop/adm2_weights_u5.rda'))
}

```


<!-- Load model data -->

```{r load_cluster_dat}

if(strata.model == "strat"){
  load(paste0(data.dir, '/', country, '_cluster_dat_1frame.rda'), 
       envir = .GlobalEnv)
}else{
  load(paste0(data.dir, '/', country, '_cluster_dat.rda'),
       envir = .GlobalEnv)
}

end.year <- max(mod.dat$survey)

## Define a bunch of time parameters!
if(((end.year-beg.year+1) %% 3) == 0){
  beg.period.years <- seq(beg.year, end.year, 3) 
  end.period.years <- beg.period.years + 2 
}else if(((end.year-beg.year+1) %% 3) == 1){
  beg.period.years <- c(beg.year, beg.year+2,
                        seq(beg.year+4,end.year, 3))
  end.period.years <- c(beg.year+1, beg.year+3,
                        seq(beg.year+6,end.year, 3))
}else if(((end.year-beg.year+1) %% 3) == 2){
  beg.period.years <- c(beg.year, seq(beg.year+2, end.year, 3))
  end.period.years <- c(beg.year+1,seq(beg.year+4, end.year, 3))
}
```

# Intro

These estimates are created using `r ifelse(strata.model == "unstrat", "an unstratified", "a stratified")` BB8 model with subnational estimates using a `r toupper(time.model)` main temporal effect and a `r toupper(time.model)`xICAR spatiotemporal interaction term with area-specific random slopes. \par


`r country` has `r nrow(admin1.names)` Admin 1 areas and `r nrow(admin2.names)` Admin 2 areas.\par


All uncertainty intervals displayed in subsequent figures are 95\% intervals.


# National Survey Data
```{r sumstat, echo = F,results='asis', warning=FALSE}
levels(mod.dat$urban) <- tolower(levels(mod.dat$urban))

mod.dat$survey.table <- paste(mod.dat$survey.type,
                              mod.dat$survey, sep = " ")
clus.table <- aggregate(cluster ~ survey.table + urban,
                        data = mod.dat,
                        FUN = function(x){length(unique(x))})
clus.xtable <- reshape(clus.table,
                       v.names = "cluster",
                       idvar = "survey.table",
                       timevar = "urban",
                       direction = "wide")
clus.xtable$Total <- clus.xtable$cluster.urban + 
  clus.xtable$cluster.rural
row.names(clus.xtable) <- clus.xtable[,'survey.table']

colnames(clus.xtable) <- c("Survey", "Urban",
                           "Rural", "Total")
clus.printxtable <- xtable(clus.xtable, 
                           digits = c(0,0,0,0,0),
                           align = "ccccc",
                           caption = paste0("Number of clusters by urban/rural designation by survey for ",
                                            country, "."))
print.xtable(clus.printxtable, 
             comment = F, 
             include.rownames = F)

sum.table <- aggregate(cbind(Y, total) ~ survey.table + age,
                       data = mod.dat,
                       FUN = sum)
sum.tableList <- list()

surveys <- unique(mod.dat$survey.table) %>% sort()

for(idx in 1:length(surveys)){
  survey <- surveys[idx]
  sum.tableList[[idx]] <- sum.table[sum.table$survey.table == survey,-1]
  names(sum.tableList[[idx]]) <- c("Age", 
                                   "No. Deaths",
                                   "No. Agemonths")
  
  sum.print <- xtable(sum.tableList[[idx]],
                      digits = c(0,0,0,0),
                      align = "cccc", 
                      caption = paste0("Numbers of agemonths and deaths by age for ",
                                       survey, "."))
  print.xtable(sum.print,
               comment = F,
               include.rownames = F,
               table.placement = "!ht")
}
```

# National Figures and Results

<!-- ```{r, results ='asis', echo = FALSE} -->
<!-- load(paste0(dir.path, '/', -->
<!--             folder.name, '/', -->
<!--             country, -->
<!--             '_rw2_natl_noStrata_fixed.rda')) -->
<!-- coefs <- fixed.eff -->

<!-- load(paste0(dir.path, '/', -->
<!--             folder.name, '/', -->
<!--             country, -->
<!--             '_rw2_natlBench_noStrata_fixed.rda')) -->
<!-- coefs.bench <- fixed.eff -->

<!-- coefs$tab <- paste0("(", -->
<!--                     round(expit(coefs$`0.025quant`)*1000,1), -->
<!--                     ",", -->
<!--                     round(expit(coefs$`0.975quant`)*1000,1), -->
<!--                     ")") -->
<!-- coefs <- coefs[,c("0.5quant", "tab")] -->
<!-- coefs$`0.5quant` <- round(expit(coefs$`0.5quant`)*1000,1) -->

<!-- coefs.bench$tab <- paste0("(", -->
<!--                           round(expit(coefs.bench$`0.025quant`)*1000,1), -->
<!--                           ",", -->
<!--                           round(expit(coefs.bench$`0.975quant`)*1000,1), -->
<!--                           ")") -->
<!-- coefs.bench <- coefs.bench[,c("0.5quant", "tab")] -->
<!-- coefs.bench$`0.5quant` <- round(expit(coefs.bench$`0.5quant`)*1000,1) -->

<!-- names(coefs) <- c("Median", "Interval") -->
<!-- names(coefs.bench) <- c("Median- Bench", "Interval") -->

<!-- row.names(coefs) <- row.names(coefs.bench) <- c("0", "1-11", "12-23", -->
<!--                                                 "24-35", "36-47", "48-59") -->

<!-- coefs.xtable <- xtable(cbind.data.frame(coefs, coefs.bench), -->
<!--                        align = c("l|cc|cc"), -->
<!--                        digits = c(0,2,0,2,0), -->
<!--                        caption = paste0("Monthly hazards in terms of 1000 children by age band for national, unstratified model for ", country, ".")) -->
<!-- print.xtable(coefs.xtable, -->
<!--              comment = F) -->
<!-- ``` -->


```{r ur_odds, results = 'asis'}
bench_str <- ifelse(bench.model == "", bench.model, "_bench")
ur.odds.filename <- paste0(country, "_URodds_natl_",
                           time.model, "_", strata.model,
                           "_u5", bench_str, ".pdf")

if(!file.exists(paste0(res.dir, "/Figures/Trends/U5MR/", ur.odds.filename))){
  if(file.exists(paste0(res.dir, "/Figures/Trends/U5MR/",
                    gsub(paste0(time.model, "_"), "", ur.odds.filename)))){
    ur.odds.filename <- gsub(paste0(time.model, "_"), "", ur.odds.filename)
  }else{
    message("Cannot find the UR odds file specified.")
  }
}
cat("\\begin{figure}\n \\centering\n")
cat(paste0("\\includegraphics[width=5in]{", res.dir, 
           "/Figures/Trends/U5MR/",
           ur.odds.filename, "}\n"))
cat(paste0("\\caption{The urban rural odds from the national BB8 model.}\n",
           "\\end{figure}\n",
           "\\clearpage"))
```

```{r natl, results = 'asis'}
natl.nmr.filename <- paste0(country, "_natl_", strata.model,
                          "_", time.model, 
                           "_nmr_Spaghetti.pdf")

if(!file.exists(paste0(res.dir, "/Figures/Summary/NMR/", natl.nmr.filename))){
  if(file.exists(paste0(res.dir, "/Figures/Summary/NMR/",
                    gsub(paste0(time.model, "_"), "", natl.nmr.filename)))){
    natl.nmr.filename <- gsub(paste0(time.model, "_"), "", natl.nmr.filename)
  }else{
    message("Cannot find the national NMR file specified.")
  }
}

natl.u5.filename <- paste0(country, "_natl_", strata.model,
                          "_", time.model, 
                           "_u5_Spaghetti.pdf")

if(!file.exists(paste0(res.dir, "/Figures/Summary/U5MR/", natl.u5.filename))){
  if(file.exists(paste0(res.dir, "/Figures/Summary/U5MR/",
                    gsub(paste0(time.model, "_"), "", natl.u5.filename)))){
    natl.u5.filename <- gsub(paste0(time.model, "_"), "", natl.u5.filename)
  }else{
    message("Cannot find the national U5MR file specified.")
  }
}

cat("\\begin{figure}\n \\centering\n")
cat(paste0("\\includegraphics[width=8in]{", res.dir, 
           "/Figures/Summary/NMR/",
           natl.nmr.filename, "}\n"))
cat(paste0("\\caption{NMR results from the national BB8 model.}\n",
           "\\end{figure}\n",
           "\\clearpage"))
cat("\\begin{figure}\n \\centering\n")
cat(paste0("\\includegraphics[width=8in]{", res.dir, 
           "/Figures/Summary/U5MR/",
           natl.u5.filename, "}\n"))
cat(paste0("\\caption{U5MR results from the national BB8 model.}\n",
           "\\end{figure}\n",
           "\\clearpage"))
```

<!-- # Admin 1 Figures -->


<!-- # Admin 2 Figures -->

<!-- The following few pages have estimates by area across time with underlying data included. There are six admin areas per page. -->
<!-- <!-- ,they are ordered by increasing median U5MR in the year 2019.  --> -->
<!-- Colored lines with circular points and light grey uncertainty bands are 5-year survey-weighted estimates of U5MR for years 1990--1994 up to 2015--2019 depending on survey timing. For a survey that ends in the middle of a 5-year period, we plot the estimates at the mid-point of the years in that interval for which the survey provides data. Black lines and corresponding intervals represent posterior medians and 95\% uncertainty intervals respectively for the betabinomial model. -->
<!-- <!-- IHME's estimates and corresponding intervals, where we can compare, are in aquamarine. --> -->

<!-- \includepdf[pages=-]{/Users/j_godwin/Dropbox/AfricaAdmin2Estimates/Data/countryDataFolders/Togo/Plots/Betabinomial/Admin2/Togo_rw2main_randomSlopes_rw1xICAR_admin2Bench_noStrata_spaghetti_6per.pdf} -->

\clearpage
# Subnational Results


```{r neighb_adm1, results='asis'}

cat("\\begin{figure}\n \\centering\n")
cat(paste0("\\includegraphics[width=3.5in]{", res.dir, 
           "/Figures/ShapeCheck/",
           country, "_adm1_neighb.pdf}\n"))
cat(paste0("\\includegraphics[width=3.5in]{", res.dir, 
           "/Figures/ShapeCheck/",
           country, "_adm2_neighb.pdf}\n"))
cat(paste0("\\caption{Top: The neighborhood structure of Admin 1 areas. ",
           "Bottom: The neighborhood structure of Admin 2 areas.}\n",
           "\\end{figure}\n",
           "\\clearpage"))
```


