---
title: "Country Summary: Malawi"
output: 
  pdf_document:
    toc: true
    number_sections: true
geometry: margin=0.5in
---


<!-- Setup -->

<!-- Libraries -->

```{r libs, echo = FALSE, message=FALSE, warning=FALSE}
rm(list = ls())

options(gsubfn.engine = "R")
library(rgdal)
library(Rfast)
library(dplyr)
library(tidyr)
library(ggplot2)
library(tidyverse)
library(RColorBrewer)
library(xtable)

## knitr options
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
```

<!-- User-defined Arguments -->
```{r params}
country <- "Malawi"
debugging <- FALSE

## MIGHT NEED TO BE CHANGED depending on what you fit
time.model <- c('rw2','ar1')[2] #time model for BB8
strata.model <- c("strat", "unstrat")[1]
bench.model <- c("", "bench")[2] #this should be equal to 'bench' unless trying to troubleshoot


## Timing of projection

end.proj.year <- 2021
plot.years <- 2000:end.proj.year
n_years <- length(plot.years)
```


<!-- Working Directory -->

```{r setwd}

# set the working directory (location of this file in /Rcode)

# extract file location of this script
code.path <- rstudioapi::getActiveDocumentContext()$path
code.path.splitted <- strsplit(code.path, "/")[[1]]

home.dir <- paste(code.path.splitted[1: (length(code.path.splitted)-2)],
                  collapse = "/")

## ONLY NEED TO DO IF USING MAC -- changes user path to that of your local computer
home.dir <- fs::path_expand(home.dir)

knitr::opts_chunk$set(root.dir = home.dir)

## You need to run this line IN THE CONSOLE
## if you need to debug
if(debugging == TRUE){
  setwd(home.dir)
}

# set the directory that stores the data

data.dir <- paste0(home.dir,'/Data/', country) 

# set the directory to store the results (e.g. fitted R objects, figures, tables in .csv etc.)

res.dir <- paste0(home.dir,'/Results/', country)
```


<!-- ## Functions -->
```{r fns}
logit <- function(x){
  log(x/(1-x))
}
expit <- function(x){
  exp(x)/(1 + exp(x))
}

##### function to organize posterior draws from BB8 ####

draw_1y_adm<-function(admin_draws, year_num,admin_vec, nsim=1000){
  
  # year_num: year of comparison
  # nsim: number of posterior draws
  # admin_vec: vector of admin index
  # admin_draws: posterior draws (as a list from SUMMER output)
  
  # prepare reference frame for draws 
  # ID corresponds to specific year, region
  draw_ID<-c(1:length(admin_draws))
  draw_year<-vector()
  draw_region<-vector()
  
  for( i in draw_ID){
    tmp_d<-admin_draws[[i]]
    draw_year[i]<-tmp_d$years
    draw_region[i]<-tmp_d$region
  }
  
  draw_ref<-data.frame(id=draw_ID,year=draw_year,
                       region=draw_region)
  
  draw_frame<-matrix( nrow = nsim, ncol = length(admin_vec))
  
  for(i in 1:length(admin_vec)){
    admin_i<-admin_vec[i]
    id_draw_set<-draw_ref[draw_ref$year==year_num&
                            draw_ref$region==admin_i,]$id 
    
    draw_set<-admin_draws[[id_draw_set]]$draws
    
    draw_frame[,i]<-draw_set
    #print(mean(r_frame[,c(admin_i)]))
  }
  
  colnames(draw_frame)<-admin_vec
  
  return(draw_frame)
}

```

<!-- # Load Data: Country Info -->


```{r load_countryinfo, echo = FALSE}
info.name <- paste0(country, "_general_info.Rdata")

# load the country info

info.name <- paste0(country, "_general_info.Rdata")
load(file = paste0(home.dir, '/Info/', info.name, sep=''))
```

<!-- #### Load admin names  ------------------------------------------------------ -->

```{r load adminnames}
load(paste0(data.dir, '/',poly.path,'/', country, '_Amat.rda'))
load(paste0(data.dir, '/', poly.path,'/', country, '_Amat_Names.rda'))
```



<!-- #### load admin1 and admin2 weights #### -->
```{r load adminwts}
load(paste0(data.dir,'/worldpop/adm1_weights_u1.rda'))
load(paste0(data.dir,'/worldpop/adm1_weights_u5.rda'))
if(exists('poly.layer.adm2')){
  load(paste0(data.dir,'/worldpop/adm2_weights_u1.rda'))
  load(paste0(data.dir,'/worldpop/adm2_weights_u5.rda'))
}

```


<!-- Load model data -->

```{r load cluster dat}

if(strata.model == "strat"){
  load(paste0(data.dir, '/', country, '_cluster_dat_1frame.rda'), 
       envir = .GlobalEnv)
}else{
  load(paste0(data.dir, '/', country, '_cluster_dat.rda'),
       envir = .GlobalEnv)
}

end.year <- max(mod.dat$survey)

## Define a bunch of time parameters!
if(((end.year-beg.year+1) %% 3) == 0){
  beg.period.years <- seq(beg.year, end.year, 3) 
  end.period.years <- beg.period.years + 2 
}else if(((end.year-beg.year+1) %% 3) == 1){
  beg.period.years <- c(beg.year, beg.year+2,
                        seq(beg.year+4,end.year, 3))
  end.period.years <- c(beg.year+1, beg.year+3,
                        seq(beg.year+6,end.year, 3))
}else if(((end.year-beg.year+1) %% 3) == 2){
  beg.period.years <- c(beg.year, seq(beg.year+2, end.year, 3))
  end.period.years <- c(beg.year+1,seq(beg.year+4, end.year, 3))
}
```

# Intro

These estimates are created using `r ifelse(strata.model == "unstrat", "an unstratified", "a stratified")` BB8 model with subnational estimates using a `r toupper(time.model)` main temporal effect and a `r toupper(time.model)`xICAR spatiotemporal interaction term with area-specific random slopes. \par

```{r,  results='asis'}
if(exists('poly.layer.adm2')){
  cat("\n",country, ' has ', nrow(admin1.names), ' Admin 1 areas and ', nrow(admin2.names), 'Admin 2 areas. \n')
}else{
   cat("\n", country, ' has ', nrow(admin1.names), ' Admin 1 areas. \n')
}
```


All uncertainty intervals displayed in subsequent figures are 90\% intervals.


# National Data Summaries and Results

## Survey data
```{r sumstat, echo = F,results='asis', warning=FALSE}
levels(mod.dat$urban) <- tolower(levels(mod.dat$urban))

mod.dat$survey.table <- paste(mod.dat$survey.type,
                              mod.dat$survey, sep = " ")
clus.table <- aggregate(cluster ~ survey.table + urban,
                        data = mod.dat,
                        FUN = function(x){length(unique(x))})
clus.xtable <- reshape(clus.table,
                       v.names = "cluster",
                       idvar = "survey.table",
                       timevar = "urban",
                       direction = "wide")
clus.xtable$Total <- clus.xtable$cluster.urban + 
  clus.xtable$cluster.rural
row.names(clus.xtable) <- clus.xtable[,'survey.table']

colnames(clus.xtable) <- c("Survey", "Urban",
                           "Rural", "Total")
clus.printxtable <- xtable(clus.xtable, 
                           digits = c(0,0,0,0,0),
                           align = "ccccc",
                           caption =
                             paste0("Number of clusters by urban/rural ",
                                    "designation by survey for ", country, "."))
print.xtable(clus.printxtable, 
             comment = F, 
             include.rownames = F)

sum.table <- aggregate(cbind(Y, total) ~ survey.table + age,
                       data = mod.dat,
                       FUN = sum)
sum.tableList <- list()

surveys <- unique(mod.dat$survey.table) %>% sort()

for(idx in 1:length(surveys)){
  survey <- surveys[idx]
  sum.tableList[[survey]] <- sum.table[sum.table$survey.table == survey,-1]
  names(sum.tableList[[survey]]) <- c("Age", 
                                   "No. Deaths",
                                   "No. Agemonths")
}

attr(sum.tableList, "subheadings") <- names(sum.tableList)
  
sum.print <- xtableList(sum.tableList,
                       digits = c(0,0,0,0),
                       align = "cccc", 
                       caption = paste0("Numbers of agemonths and deaths by ",
                                        "age group for each survey used ",
                                        "in analysis for ", country, "."))
print.xtableList(sum.print,
                 comment = F,
                 include.rownames = F,
                 table.placement = "!ht",
                 colnames.format = "multiple")
```


```{r coefs, results ='asis', echo = FALSE}
bench_str <- ifelse(bench.model == "", bench.model, "_bench")

if(strata.model == "strat"){
  fixed.filename <- paste0(country, "_fixed_adm1_",
                           time.model, "_", strata.model,
                           "_u5", bench_str, ".rda")
}else{
  fixed.filename <- paste0(country, "_fixed_adm1_",
                           time.model, "_", strata.model,
                           "_u5_allsurveys", bench_str, ".rda")

}

if(!file.exists(paste0(res.dir, "/Betabinomial/U5MR/",
                       fixed.filename))){
  if(file.exists(paste0(res.dir, "/Betabinomial/U5MR/",
                    gsub(paste0(time.model, "_"), "", fixed.filename)))){
    fixed.filename <- gsub(paste0(time.model, "_"), "", fixed.filename)
    message("Loading fixed effects from the file\n", fixed.filename, "\n")
  }else{
    message("Cannot find the fixed effects file specified.")
  }
}else{
 message("Loading fixed effects from the file\n", fixed.filename, "\n")  
}


load(paste0(res.dir, "/Betabinomial/U5MR/", fixed.filename))

if(strata.model == "unstrat"){
  if(bench.model == ""){
    coefs <- bb.fixed.adm1.unstrat.u5.allsurveys
  }else{
    coefs <- bb.fixed.adm1.unstrat.u5.allsurveys.bench
  }
}else{
  if(bench.model == ""){
    coefs <- bb.fixed.adm1.strat.u5
  }else{
    coefs <- bb.fixed.adm1.strat.u5.bench
  }
}
coefs$tab <- paste0("(",
                    round(expit(coefs$`0.025quant`)*1000,1),
                    ",",
                    round(expit(coefs$`0.975quant`)*1000,1),
                    ")")
coefs <- coefs[,c("0.5quant", "tab")]
coefs$`0.5quant` <- round(expit(coefs$`0.5quant`)*1000,1)
names(coefs) <- c("Median", "Interval")

if(strata.model == "strat"){
coefs_tab <- coefs %>% 
  mutate(varname = row.names(coefs)) %>% 
  filter(grepl("age", varname)) %>% 
  mutate(Urban = substr(varname, nchar(varname) - 5 + 1, nchar(varname))) %>% 
  mutate(varname = gsub("age.intercept", "", varname),
         varname = gsub(":urban", "", varname),
         varname = gsub(":rural", "", varname)) %>%
  pivot_wider(id_cols = varname,
              names_from = "Urban",
              values_from = Interval) %>%  
  rename("Age" = "varname") %>% 
  as.data.frame()
}else{
  coefs_tab <- coefs %>% 
  mutate(varname = row.names(coefs)) %>% 
  filter(grepl("age", varname)) %>% 
   mutate(varname = gsub("age.intercept", "", varname),
         varname = gsub(":urban", "", varname),
         varname = gsub(":rural", "", varname)) %>%  
  rename("Age" = "varname") %>% 
    as.data.frame()
}

bench_cap_str <- ifelse(bench.model == "", "unbenchmarked", "benchmarked")
strata_cap_str <- ifelse(strata.model == "unstrat", "unstratified",
                         "stratified")
coefs.xtable <- xtable(coefs_tab,
                       align = c("ll|cc"),
                       digits = c(0,0, 0,0),
                       caption =
                         paste0("The 95\\% credible intervals for monthly ", 
                                "hazards in terms of 1000 ",
                                "children by age band for the Admin-1, ",
                                bench_cap_str, " ", strata_cap_str,
                                " model for ",
                                country, "."))
print.xtable(coefs.xtable, 
             comment = F, 
             include.rownames = F,
             table.placement = "ht")
```

\clearpage

## Figures

```{r urodds, results='asis'}
if(strata.model == 'strat'){

ur.odds.filename <- paste0(country, "_URodds_natl_",
                           time.model, "_", strata.model,
                           "_u5.pdf")

if(!file.exists(paste0(res.dir, "/Figures/Trends/U5MR/", ur.odds.filename))){
  if(file.exists(paste0(res.dir, "/Figures/Trends/U5MR/",
                    gsub(paste0(time.model, "_"), "", ur.odds.filename)))){
    ur.odds.filename <- gsub(paste0(time.model, "_"), "", ur.odds.filename)
  }else{
    message("Cannot find the UR odds file specified.")
  }
}
cat("\\begin{figure}\n \\centering\n")
 cat(paste0("\\includegraphics[width=5in]{", res.dir,
            "/Figures/Trends/U5MR/",
            ur.odds.filename, "}\n"))
 cat(paste0("\\caption{Urban rural odds ratio from stratified national model.}\n",
            "\\end{figure}\n",
            "\\clearpage"))
}
```


```{r natl, results = 'asis'}
natl.nmr.filename <- paste0(country, "_natl_", strata.model,
                          "_", time.model,
                           "_nmr_Spaghetti.pdf")

if(!file.exists(paste0(res.dir, "/Figures/Summary/NMR/", natl.nmr.filename))){
  if(file.exists(paste0(res.dir, "/Figures/Summary/NMR/",
                    gsub(paste0(time.model, "_"), "", natl.nmr.filename)))){
    natl.nmr.filename <- gsub(paste0(time.model, "_"), "", natl.nmr.filename)
  }else{
    message("Cannot find the national NMR file specified.")
  }
}

natl.u5.filename <- paste0(country, "_natl_", strata.model,
                          "_", time.model,
                           "_u5_Spaghetti.pdf")

if(!file.exists(paste0(res.dir, "/Figures/Summary/U5MR/", natl.u5.filename))){
  if(file.exists(paste0(res.dir, "/Figures/Summary/U5MR/",
                    gsub(paste0(time.model, "_"), "", natl.u5.filename)))){
    natl.u5.filename <- gsub(paste0(time.model, "_"), "", natl.u5.filename)
  }else{
    message("Cannot find the national U5MR file specified.")
  }
}

cat("\\begin{figure}\n \\centering\n")
cat(paste0("\\includegraphics[width=7.5in]{", res.dir,
           "/Figures/Summary/NMR/",
           natl.nmr.filename, "}\n"))
cat(paste0("\\caption{NMR results from the national BB8 model.}\n",
           "\\end{figure}\n"))
cat("\\begin{figure}\n \\centering\n")
cat(paste0("\\includegraphics[width=7.5in]{", res.dir,
           "/Figures/Summary/U5MR/",
           natl.u5.filename, "}\n"))
cat(paste0("\\caption{U5MR results from the national BB8 model.}\n",
           "\\end{figure}\n",
           "\\clearpage"))
```

\clearpage

# Subnational Results


```{r neighbadm1, results='asis'}
if(exists('poly.layer.adm2')){
cat("\\begin{figure}[!h]\n \\centering\n")
cat(paste0("\\includegraphics[width=3.5in]{", res.dir,
           "/Figures/ShapeCheck/",
           country, "_adm1_neighb.pdf}\n"))
cat(paste0("\\includegraphics[width=3.5in]{", res.dir,
           "/Figures/ShapeCheck/",
           country, "_adm2_neighb.pdf}\n"))
cat(paste0("\\caption{Top: The neighborhood structure of Admin 1 areas. ",
           "Bottom: The neighborhood structure of Admin 2 areas.}\n",
           "\\end{figure}\n"))
}else{
  cat("\\begin{figure}[!h]\n \\centering\n")
cat(paste0("\\includegraphics[width=3.5in]{", res.dir,
           "/Figures/ShapeCheck/",
           country, "_adm1_neighb.pdf}\n"))
cat(paste0("\\caption{The neighborhood structure of Admin 1 areas.}\n",
           "\\end{figure}\n"))
}
```


## Admin 1 Figures

```{r adm1, results = 'asis'}
adm1.nmr.filename <- paste0(country, "_adm1_", time.model, "_",
                            strata.model, "_nmr", bench_str,
                            "_", "medianmap_20002021.pdf")

if(!file.exists(paste0(res.dir, "/Figures/Summary/NMR/", adm1.nmr.filename))){
    message("Cannot find the Admin-1 NMR file specified.")
}

adm1.u5.filename <- paste0(country, "_adm1_", time.model, "_",
                            strata.model, "_u5", bench_str,
                            "_medianmap_20002021.pdf")

if(!file.exists(paste0(res.dir, "/Figures/Summary/U5MR/", adm1.u5.filename))){
    message("Cannot find the Admin-1 U5MR file specified.")
}


cat("\\begin{figure}[!h]\n \\centering\n")
cat(paste0("\\includegraphics[width=3.5in]{", res.dir,
           "/Figures/Summary/NMR/",
           adm1.nmr.filename, "}\n"))
cat(paste0("\\includegraphics[width=3.5in]{", res.dir,
           "/Figures/Summary/U5MR/",
           adm1.u5.filename, "}\n"))
cat(paste0("\\caption{NMR (left) and U5MR (right) ",
           "results in 2000, 2010, 2015, and 2021 ",
           "from the Admin-1 BB8 model.}\n",
           "\\end{figure}\n",
           "\\clearpage"))
```

```{r adm1spag, results = 'asis', fig.cap = "Median NMR estimates by Admin-1 from the BB8 model."}

adm1.nmr.filenames <- list.files(paste0(res.dir, "/Figures/Summary/NMR/"))
adm1.nmr.filenames <- adm1.nmr.filenames[grepl("_Admin1_nmr_SpaghettiAll_",
                                               adm1.nmr.filenames)]
if(bench.model == ""){
  adm1.nmr.filenames <- adm1.nmr.filenames[grepl(time.model, adm1.nmr.filenames) &
                                           grepl(paste0("_", strata.model,
                                                        "_"),
                                                 adm1.nmr.filenames) &
                                           !grepl("bench", adm1.nmr.filenames)] %>%
  sort()
}else{
adm1.nmr.filenames <- adm1.nmr.filenames[grepl(time.model, adm1.nmr.filenames) &
                                           grepl(paste0("_", strata.model,
                                                        "_",bench.model,"_"),
                                                 adm1.nmr.filenames)] %>%
  sort()
}


if(length(adm1.nmr.filenames) == 0){
    message("Cannot find the Admin-1 NMR file specified.")
}


adm1.u5.filenames <- list.files(paste0(res.dir, "/Figures/Summary/U5MR/"))
adm1.u5.filenames <- adm1.u5.filenames[grepl("_Admin1_u5_SpaghettiAll_",
                                               adm1.u5.filenames)]
if(bench.model == ""){
  adm1.u5.filenames <- adm1.u5.filenames[grepl(time.model, adm1.u5.filenames) &
                                           grepl(paste0("_", strata.model,
                                                        "_"),
                                                 adm1.u5.filenames) &
                                           !grepl("bench", adm1.u5.filenames)] %>%
  sort()
}else{
adm1.u5.filenames <- adm1.u5.filenames[grepl(time.model, adm1.u5.filenames) &
                                           grepl(paste0("_", strata.model,
                                                        "_",bench.model,"_"),
                                                 adm1.u5.filenames)] %>%
  sort()
}

if(length(adm1.u5.filenames) == 0){
    message("Cannot find the Admin-1 U5MR file specified.")
}

for(nmr.file in adm1.nmr.filenames){
cat("\\begin{figure}[!h]\n \\centering\n")
cat(paste0("\\includegraphics[width=7.5in]{", res.dir,
           "/Figures/Summary/NMR/",
           nmr.file, "}\n"))
cat(paste0("\\end{figure}\n"))
}
cat("\\clearpage")
```

```{r adm1spagu5, results = "asis", fig.cap = "Median U5MR estimates by Admin-1 from the BB8 model."}
for(u5.file in adm1.u5.filenames){
cat("\\begin{figure}[!h]\n \\centering\n")
cat(paste0("\\includegraphics[width=7.5in]{", res.dir,
           "/Figures/Summary/U5MR/",
           u5.file, "}\n"))
cat(paste0("\\end{figure}\n"))
}
```

\clearpage

```{r adm2, results = 'asis'}
if(exists('poly.layer.adm2')){
  cat("\n## Admin 2 Figures\n")
adm2.nmr.filename <- paste0(country, "_adm2_", time.model, "_",
                            strata.model, "_nmr", bench_str,
                            "_", "medianmap_20002021.pdf")

if(!file.exists(paste0(res.dir, "/Figures/Summary/NMR/", adm2.nmr.filename))){
    message("Cannot find the Admin-2 NMR file specified.")
}

adm2.u5.filename <- paste0(country, "_adm2_", time.model, "_",
                            strata.model, "_u5", bench_str,
                            "_medianmap_20002021.pdf")

if(!file.exists(paste0(res.dir, "/Figures/Summary/U5MR/", adm2.u5.filename))){
    message("Cannot find the Admin-2 U5MR file specified.")
}


cat("\\begin{figure}[!h]\n \\centering\n")
cat(paste0("\\includegraphics[width=3.5in]{", res.dir,
           "/Figures/Summary/NMR/",
           adm2.nmr.filename, "}\n"))
cat(paste0("\\includegraphics[width=3.5in]{", res.dir,
           "/Figures/Summary/U5MR/",
           adm2.u5.filename, "}\n"))
cat(paste0("\\caption{NMR (left) and U5MR (right) ",
           "results in 2000, 2010, 2015, and 2021 ",
           "from the Admin-2 BB8 model.}\n",
           "\\end{figure}\n",
           "\\clearpage"))
}
```

```{r adm2spag, results = 'asis',fig.cap = "Median NMR estimates by Admin-2 from the BB8 model."}
if(exists('poly.layer.adm2')){
adm2.nmr.filenames <- list.files(paste0(res.dir, "/Figures/Summary/NMR/"))
adm2.nmr.filenames <- adm2.nmr.filenames[grepl("_Admin2_nmr_SpaghettiAll_",
                                               adm2.nmr.filenames)]
if(bench.model == ""){
  adm2.nmr.filenames <- adm2.nmr.filenames[grepl(time.model, adm2.nmr.filenames) &
                                           grepl(paste0("_", strata.model,
                                                        "_"),
                                                 adm2.nmr.filenames) &
                                           !grepl("bench", adm2.nmr.filenames)] %>%
  sort()
}else{
adm2.nmr.filenames <- adm2.nmr.filenames[grepl(time.model, adm2.nmr.filenames) &
                                           grepl(paste0("_", strata.model,
                                                        "_",bench.model,"_"),
                                                 adm2.nmr.filenames)] %>%
  sort()
}

if(length(adm2.nmr.filenames) == 0){
    message("Cannot find the Admin-2 NMR file specified.")
}


adm2.u5.filenames <- list.files(paste0(res.dir, "/Figures/Summary/U5MR/"))
adm2.u5.filenames <- adm2.u5.filenames[grepl("_Admin2_u5_SpaghettiAll_",
                                               adm2.u5.filenames)]
if(bench.model == ""){
  adm2.u5.filenames <- adm2.u5.filenames[grepl(time.model, adm2.u5.filenames) &
                                           grepl(paste0("_", strata.model,
                                                        "_"),
                                                 adm2.u5.filenames) &
                                           !grepl("bench", adm2.u5.filenames)] %>%
  sort()
}else{
adm2.u5.filenames <- adm2.u5.filenames[grepl(time.model, adm2.u5.filenames) &
                                           grepl(paste0("_", strata.model,
                                                        "_",bench.model,"_"),
                                                 adm2.u5.filenames)] %>%
  sort()
}


if(length(adm2.u5.filenames) == 0){
    message("Cannot find the Admin-2 U5MR file specified.")
}

for(nmr.file in adm2.nmr.filenames){
cat("\\begin{figure}[!h]\n \\centering\n")
cat(paste0("\\includegraphics[width=7.5in]{", res.dir,
           "/Figures/Summary/NMR/",
           nmr.file, "}\n"))
cat(paste0("\\end{figure}\n"))
}
cat("\\clearpage")
}
```
```{r adm2spagu5, results = "asis", fig.cap = "Median U5MR estimates by Admin-2 from the BB8 model."}
if(exists('poly.layer.adm2')){
for(u5.file in adm2.u5.filenames){
cat("\\begin{figure}[!h]\n \\centering\n")
cat(paste0("\\includegraphics[width=7.5in]{", res.dir,
           "/Figures/Summary/U5MR/",
           u5.file, "}\n"))
cat(paste0("\\end{figure}\n"))
}
}
```
